Near and Mid-infrared properties of known redshift $z\geq5$ Quasars

### 2019-06-14 tex/VHzQ.tex
tables_for_paper/output_table_top5pc.tex

Figure~\ref{fig:coverage} shows the areal coverage of the ULAS, UHS,
VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR11
3,700 deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
deg$^{2}$. The overlap between UHS DR1 and VHS DR6 is 28 deg. These
four surveys together cover 33,000 deg$^{2}$.

@@

\begin{landscape}
      \input{../tables_for_paper/output_table}
\end{landscape}

>>>>

Figure~\ref{fig:coverage} shows the areal coverage of the ULAS, UHS,
VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR1 3,700
deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
deg$^{2}$. The overlap between UHS DR1 and VHS DR6 is 28 deg. These
four surveys together cover 33,000 deg$^{2}$. VHS, ULAS and UHS do not
observe in the $Z$-band.

@@

\begin{landscape}
      \input{../tables_for_paper/output_table_top5pc}
\end{landscape}
